### 2016-03-09 thesis/conclusions.tex
sleep

Chapter \ref{ch:galviv} \citep{paperI} was dedicated to the careful multicomponent decomposition of 66 galaxies 
with a direct measurement of the black hole mass. 
We followed the same approach as \citet{laurikainen2005} in selecting the components for each galaxy model.  
\emph{A priori} identification of the galaxy components was done on the basis of several different indicators 
such as the analysis of the isophotal parameters, 
the inspection of unsharp masks, 
complementary information extracted from the literature, 
and -- most importantly -- from the galaxy kinematics. 
A joint photometric-kinematic approach (e.g.~\citealt{krajnovic2013,arnold2014}) 
turned out to play a decisive role for the robustness of our galaxy modelling. 
Upon examining central \citep{atlas3dIII,scott2014} and more extended \citep{arnold2014} velocity maps 
and comparing kinematic and photometric signatures of stellar discs, 
we were able to securely identify the presence and the radial extent of such discs. 
We observed a wide range of spheroid-to-disc ratios in early-type galaxies, 
going from parsec-sized nuclear discs, to kiloparsec-sized intermediate- and large-scale discs, 
in agreement with the findings of \citet{krajnovic2013}. 
Comparison of our results with those obtained by previous studies indicates that 
multicomponent models (as opposed to simple bulge/disc models) are necessary 
to derive reliable structural parameters, confirming previous results 
(e.g.~\citealt{laurikainen2005,laurikainen2007,laurikainen2010,lasker2014data,salo2015}). 
In general, the best-fit parameters obtained with 1D and 2D decomposition techniques for the same galaxy 
are consistent with each other, 
i.e.~no systematic effects were noticed between 1D and 2D modelling. 
However, our practical experience led us to prefer the 1D decomposition technique. 
Advantages associated with the 1D technique are a higher convergence rate for the fits, 
the wealth of information contained in the 1D isophotal analysis, 
and the easier interpretation of the 1D residuals. 
We caution against the dangerous practice of identifying unsubtracted galaxy components 
from the residual image of a 2D fit. 
As an additional warning, 
given the level of detail to which our galaxy decompositions were carried out, 
we do not consider possible for current automatic routines to reproduce our analysis. \\
future: bayes analysis to estimate max number of components, comparison with "physical" components; 
improving kin-phot approach, large kin maps are needed, 
combining hst + wide field obs to map galaxy outskirts, 
use bayes analysis to estimate uncertainties on params so that we don't need other decompositions, 
use of isofit and boggy's code for decomp, \\

>>>>

Chapter \ref{ch:galviv} \citep{paperI} was dedicated to the careful multicomponent decomposition of 66 galaxies 
with a direct measurement of the black hole mass. 
We followed the same approach as \citet{laurikainen2005} in selecting the components for each galaxy model.  
\emph{A priori} identification of the galaxy components was done on the basis of several different indicators 
such as the analysis of the isophotal parameters, 
the inspection of unsharp masks, 
complementary information extracted from the literature, 
and -- most importantly -- from the galaxy kinematics. 
A joint photometric-kinematic approach (e.g.~\citealt{krajnovic2013,arnold2014}) 
turned out to play a decisive role for the robustness of our galaxy modelling. 
Upon examining central \citep{atlas3dIII,scott2014} and more extended \citep{arnold2014} velocity maps 
and comparing kinematic and photometric signatures of stellar discs, 
we were able to securely identify the presence and the radial extent of such discs. 
We observed a wide range of spheroid-to-disc ratios in early-type galaxies, 
going from parsec-sized nuclear discs, to kiloparsec-sized intermediate- and large-scale discs, 
in agreement with the findings of \citet{krajnovic2013}. 
Comparison of our results with those obtained by previous studies indicates that 
multicomponent models (as opposed to simple bulge/disc models) are necessary 
to derive reliable structural parameters, confirming previous results 
(e.g.~\citealt{laurikainen2005,laurikainen2007,laurikainen2010,lasker2014data,salo2015}). 
In general, the best-fit parameters obtained with 1D and 2D decomposition techniques for the same galaxy 
are consistent with each other, 
i.e.~no systematic effects were noticed between 1D and 2D modelling. 
However, our practical experience led us to prefer the 1D decomposition technique. 
Advantages associated with the 1D technique are a higher convergence rate for the fits, 
the wealth of information contained in the 1D isophotal analysis, 
and the easier interpretation of the 1D residuals. 
We caution against the dangerous practice of identifying unsubtracted galaxy components 
from the residual image of a 2D fit. 
As an additional warning, 
given the level of detail to which our galaxy decompositions were carried out, 
we do not consider possible for current automatic routines to reproduce our analysis. \\
In our 1D galaxy decomposition code, the minimisation routine is based on the Levenberg-Marquardt algorithm, 
which is known to be one of the fastest algorithms available, 
but is also prone to ``get trapped'' into local minima of the chi-squared distribution. 
As a future project, it would be interesting to implement in the code different minimisation algorithms, 
such as those available in {\tt Imfit} \citep{imfit},  
and test their performance. 
It would also be beneficial to create a procedure to estimate the systematic uncertainties 
associated with the best-fit parameters from the fit itself, 
without the need to resort to decompositions performed by other authors as we did in this work. 
One of the issues associated with multicomponent decomposition is the risk of ``overfitting'', 
i.e.~having a model with more components (or parameters) than what is actually needed. 
Information theory and Bayes analysis provide us with a number of methods 
to estimate the maximum number of parameters required by a model 
to fit a given dataset, 
such as the \citep{akaike1974} Information Criterion that we used in Chapter \ref{ch:mn}. 
One could check whether or not these methods agree with our human-supervised selection 
of ``physically motivated'' model components.

improving kin-phot approach, large kin maps are needed, 
combining hst + wide field obs to map galaxy outskirts, 
use of isofit and boggy's code for decomp, \\
